---
title: "Poject-3"
author: "Group 1"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Loading required R-packages
```{r}
library(dplyr)
library(rsvg)
library(ggimage)
library(ggplot2)
library(tibble)
library(cvms)
library(GGally)
library(olsrr)
library(arm)
```
#Load and glimpse data
```{r}
df <- read.csv("~/Documents/Collegiate/Spring_2022/MATH_456/essays/project_2/R-env/project-2/proj-3-data/age_known_titatic.csv")
glimpse(df)
```
#Check Distribution of Continuous Variables
```{r}
continuous <-select_if(df, is.numeric)
summary(continuous)
```
#Data inspection
```{r}
ggplot(continuous, aes(x = Age))+geom_density(alpha = .4, fill = "#FF6666")
ggplot(continuous, aes(x = PClass))+geom_bar(alpha = 0.8, fill = "#00AAFF")
ggplot(continuous, aes(x = Sex))+geom_bar(alpha = 0.8, fill = "#01AA33")
ggplot(continuous, aes(x = Survived))+geom_bar(alpha = 0.8, fill = "#8845EE")
```
#Visualize Correlation
```{r}
# Convert data to numeric if not already
corr <- df
# Plot the graphg
    ggcorr(corr,
    method = c("pairwise", "spearman"),
    nbreaks = 6,
    hjust = 0.8,
    label = TRUE,
    label_size = 3,
    color = "grey50")
```
#Age Versus Survival
```{r}
ggplot(df, aes(x = Age, y = Survived))+geom_point()
```
#Split Data into Train and Test
```{r}
## 75% of the sample size
set.seed(1234)
smp_size <- floor(0.75 * nrow(df))
train_ind <- sample(seq_len(nrow(df)), size = smp_size)
train <- df[train_ind, ]
test <- df[-train_ind, ]
```
#Build Model
```{r}
model_with_age <- glm(Survived ~ Age + PClass + Sex, data = train, family = 'binomial')
model_without_age <- glm(Survived ~ PClass + Sex, data = train, family = 'binomial')
```
#Outcome of prediction
```{r}
predicted.data <- data.frame(
  probability.of.Survived = model_with_age$fitted.values, 
  Survived = train$Survived
)
predicted.data <- predicted.data[
  order(predicted.data$probability.of.Survived, decreasing = FALSE),]
predicted.data$rank <- 1:nrow(predicted.data)

ggplot(data = predicted.data, aes(x = rank, y=probability.of.Survived))+
  geom_point(aes(color = Survived), alpha = 0.8, shape = 4, stroke = 1)+
  xlab("Index")+
  ylab("Predicted probability of Survival")
```
#Model Summary with age
```{r}
summary(model_with_age)
plot(model_with_age)
```
#Model Summary without age
```{r}
summary(model_without_age)
plot(model_without_age)
```
#Binned residual plot for model with age
```{r}
#Majority of data points fall within standard error bands
binnedplot(fitted(model_with_age), 
           residuals(model_with_age, type = "response"), 
           nclass = NULL, 
           xlab = "Expected Values", 
           ylab = "Average residual", 
           main = "Binned residual plot", 
           cex.pts = 0.8, 
           col.pts = 1, 
           col.int = "gray")
```
#Binnedplot for model without age
```{r}
#Majority of data points fall within standard error bands
binnedplot(fitted(model_without_age), 
           residuals(model_without_age, type = "response"), 
           nclass = NULL, 
           xlab = "Expected Values", 
           ylab = "Average residual", 
           main = "Binned residual plot", 
           cex.pts = 0.8, 
           col.pts = 1, 
           col.int = "gray")
```
#Pseudo R^2
```{r}
ll.null <- model_with_age$null.deviance/-2
ll.proposed <- model_with_age$deviance/-2
(ll.null - ll.proposed) / ll.null
```
#P-value of R^2
```{r}
1-pchisq(2*(ll.proposed - ll.null), df = (length(model_with_age$coefficients)-1))
#so we know our R^2 is accurate
```
#Plotting Confusion Matrices
```{r}
predict.1 <- predict(model_with_age, test, type = 'response')
#simple table
table_mat.1 <- table(test$Survived, predict.1 > 0.5)
# confusion matrix
f.1 <- tibble("target" = test$Survived,
            "prediction" = ifelse(predict.1 > 0.5, 1, 0))
f.1_table <- table(f.1)
cfm.1 <- as_tibble(f.1_table)
plot_confusion_matrix(cfm.1, target_col = "target", prediction_col = "prediction", counts_col = "n")

predict.2 <- predict(model_without_age, test, type = 'response')
#simple table
table_mat.2 <- table(test$Survived, predict.2 > 0.5)
# confusion matrix
f.2 <- tibble("target" = test$Survived,
            "prediction" = ifelse(predict.2 > 0.5, 1, 0))
f.2_table <- table(f.2)
cfm.2 <- as_tibble(f.2_table)
plot_confusion_matrix(cfm.2, target_col = "target", prediction_col = "prediction", counts_col = "n")
```
#Accuracy Test
```{r}
accuracy_Test.1 <- sum(diag(table_mat.1)) / sum(table_mat.1)
accuracy_Test.1
accuracy_Test.2 <- sum(diag(table_mat.2)) / sum(table_mat.2)
accuracy_Test.2
```

#Precision Vs Recall
```{r}
precision <- function(matrix) {
	# True positive
    tp <- matrix[2, 2]
	# false positive
    fp <- matrix[1, 2]
    return (tp / (tp + fp))
}
recall <- function(matrix) {
# true positive
    tp <- matrix[2, 2]# false positive
    fn <- matrix[2, 1]
    return (tp / (tp + fn))
}
prec.1 <- precision(table_mat.1)
prec.1
prec.2 <- precision(table_mat.2)
prec.2
rec.1 <- recall(table_mat.1)
rec.1
rec.2 <- recall(table_mat.2)
rec.2
```
#Harmonic Mean of precision and recall
```{r}
f1 <- 2 * ((prec.1 * rec.1) / (prec.1 + rec.1))
f1
f1.other <- 2 * ((prec.2 * rec.2) / (prec.2 + rec.2))
f1.other
```
#The ROC curve
```{r}
library(ROCR)
library(pROC)
ROCRpred <- prediction(predict.1, test$Survived)
ROCRperf <- performance(ROCRpred, 'tpr', 'fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2, 1.7))
auc_ROCR <- performance(ROCRpred, measure = "auc")
auc_ROCR <- auc_ROCR@y.values[[1]]
auc_ROCR
```
